\doublespacing

\subsection{Personnel}

% TODO: href to system-architecture
For the devised system components in our system architecture, we have agreed upon the following division of efforts:

\begin{itemize}
    \item \textbf{UI/UX \& Frontend Logic:} \textbf{\textit{Jared Amen}}
    
    Jared has worked in UI/UX and frontend logic for several different projects, ranging from start-ups to large corporations such as Instructure. He has also taken human-computer interaction and successfully designed interfaces succeeding in both form and function.
    
    \item \textbf{API/DB Interactions:} \textbf{\textit{Jaecee Naylor}}
    
    Jaecee is qualified for this because she has experience writing APIs and interacting with DBs at her internship with Intermountain Healthcare. She has also taken Databases.
    
    \item \textbf{Annotations \& Auditing:} \textbf{\textit{Jared Amen}}
    
    This system component aligns itself well with front-end work, and Jared has backend experience working for Instructure which will contribute well to any interactions that will need to take place as according to this feature. 
    
    \item \textbf{Procedural Management:} \textbf{\textit{Jaecee Naylor}}
    
    Jaecee is qualified for this because she has experience working for EnerBank, so she is already aware of necessary procedures and procedural language. She also has experience in NLP needed for more complicated overlapping tasks for more advanced document types.
    
    \item \textbf{Data Transfer \& Login Security:} \textbf{\textit{Trevor Dalton}}
    
    Trevor holds a security clearance and has experience with proprietary and secret information. He knows how to transfer information securely and without too much overhead.
    
    \item \textbf{Document Parsing \& Backend Logic:} \textbf{\textit{Trevor Dalton}}
    
    Trevor has experience with document parsing (especially in the form of PDFs) in Python and R. This knowledge will be especially helpful in parsing and finding information in the forms sent over by the users. Trevor also has experience with Backend programming in the form of the classes he has taken and work experience.
\end{itemize}

\singlespacing