\textit{As written from the perspective of one of our team members, Jaecee Naylor:}

Back in 2017 one of my neighbor’s kids managed to launch a kickball straight through my front yard window. Unfortunately, since they would not fess up I was forced to find the money for it. Like a lot of people, I did not have the money on hand to fix a window quickly. I had to apply for a loan at my credit union and it took them almost a week to get back to me. In the meantime my window was broken and there was nothing I could do but wait for the credit union to process my application. Due to fluctuating busy seasons for financial institutions, an applicant, like me, may not see a response for several days. This is because verifying documents can be a slow task for humans, but it is very possible for us to automate this task. Our Bank Document Verifier, a web application designed to integrate with financial institutions, was imagined to offer an automated solution to verify important documents to save you time, the verifications team effort, and the financial institution money. The final goal of our project is to offer an online application that financial institutions can use for document verification that is secure, fast, and customizable. Our application will be designed to verify various documents based on criteria set forth by the user, detect potentially fraudulent documents (using criteria the bank has set in place to determine fraud as well as a state-of-the-art api), and identify the type of documents sent in automatically. If a document is identified as fraudulent, the user will have the ability to annotate specific text that will be shown when a higher level of verifier views the loan application. Our application will be able to provide interpretable results and reports, store and process these documents, and save rules and templates for how to verify documents. Additionally, we will tackle more difficult documents that vary in form such as pay stubs and deeds. After finishing a session, a user will be able to save their state and log in at a later date to resume reviewing applications.

When faced with the opportunity to choose between employing dozens of employees to slog through and manually verify several thousands of documents or verify those thousands of documents accurately and swiftly, the choice and benefits thereof are clear. Within minutes, our system will provide financial institutions with a more affordable way to verify an applicant’s documents, a verification team an easier way to complete their day to day tasks, and an applicant a faster response. We know within days, customers would already be seeing the benefits of having switched to our system.