\subsection{Tools}

The following considerations have been made regarding tools used in our system. \textit{As development progresses, we expect to add more tools to this list as necessary.}

\medskip

\begin{itemize}[nosep]
    \item \textbf{IDE:} Visual Studio Code will be our primary IDE of use.
    \item \textbf{Main Library:} We have decided to use Azure for DBMS and various cloud services.
    \item \textbf{Testing Plans and Tools:} Our SCRUM sprints will be designed around testing, with the last couple days before a sprint completes being dedicated to testing. Aside from that, we might look into using tools such as Selenium for simulating typical usage of a browser to detect bugs. Additionally, test-driven development has been discussed as an option -- while more research would need to be done on the matter, it is conceivable that this would be an effective strategy for us to implement.
    
    \medskip
    
    \textit{\textbf{Our sprint meeting book is detailed out \href{https://www.notion.so/jamen/385ff019a14a48f4bb42cc0db3f455a0?v=c59fd5ba269540628a170da3666289ad}{at this link}.}}
    
    \medskip
    
    \item \textbf{Version Control:} We will continue to use the university's distribution of Gitlab for both internal and production builds of our code.
    \item \textbf{Issue Tracking:} Again, as above, the university's distribution of Gitlab will work well for us here. Additionally, we will plan out issues as stories with attached milestones, epics, weights, tags, and comment systems to easily track issues and their context.
\end{itemize}